Binary companions of evolved stars in \apogee\ \DR: \\ Search method and catalog of $\sim$5,000 companions

### 2018-04-02 paper/1-catalog/twoface-catalog.tex
Rix comments

\begin{abstract}\noindent % trust me
% Context
Multi-epoch radial velocity measurements of stars can be used to identify
stellar, sub-stellar, and planetary-mass companions.
Even a small number of observation epochs can be useful for detecting
companions, though there can be multiple qualitatively different orbital
solutions that fit the data.
For these reasons, we custom-built a Monte Carlo sampler (\thejoker) that
delivers reliable (and often highly multi-modal) posterior samplings for
companion orbital parameters given sparse radial-velocity data.
% Aims
Here we perform a search for companions to \nstars\ red-giant stars observed in
the \apogee\ survey (\DR) with $\geq 3$ spectroscopic epochs.
% Methods
We select stars with probable companions by making a cut on our posterior belief
about the amplitude of the stellar radial-velocity variation induced by the
orbit.
% Results
We provide (1)~a catalog of \nunimodal\ companions for which the stellar
companion properties can be confidently determined, (2)~a catalog of \nhighK\
stars that likely have companions, but for which more observations would be
needed to uniquely determine the orbital properties, and (3)~posterior samplings
for the full orbital parameters for all stars in the parent sample.
We highlight interesting systems and show the characteristics of systems with
confidently determined companion properties.
\end{abstract}

@@

@@

We have solved this problem previously with \thejoker\
(\citealt{Price-Whelan:2017}), a Monte Carlo rejection sampler that is
computationally expensive but probabilistically righteous:
It delivers independent posterior \pdf\ samples for single-companion binary
orbital parameters, given any number of radial-velocity measurements.
Here we use \thejoker\ to generate posterior \pdf\ samples for stars observed by
the \apogee\ survey (see \sectionname~\ref{sec:data}; \citealt{Majewski:2017}).

The \apogee\ surveys primarily target red-giant-branch (\RGB) and evolved stars,
which are ideal for the study of single-line binary systems.
In general, they are unlikely to have equally-bright companions, and their
spectra are therefore fit as single-line objects.
When this constraint is not met, \thejoker\ will in general fail, and a model
that fits for a mixture of stellar spectra is more appropriate (e.g.,
\citealt{El-Badry:2018}).
The subset of giant stars in the ``red clump'' (\RC) are even more powerful as
they are standard candles and have masses that can be estimated using
spectroscopy (using dredged-up elements; \citealt{Martig:2016,Ness:2016}).
With mass estimates for the primary star, the binary-orbit fitting will return
$M_2\,\sin i$ (minimum mass) estimates for the secondary, and not just estimates
of the so-called ``binary mass function.''
Additionally, the \apogee\ pipelines (\citealt{Garcia-Perez:2016}) and also
\thecannon\ (\citealt{Ness:2015}) produce detailed abundance estimates for \RGB\
and \RC\ stars.
If there are causal relationships between chemical abundances and binary
companions---as are expected---these should be measurable.

@@

All data used in this work comes from the publicly-available data release 14
(\DR) of the \apogee\ survey (\citealt{Majewski:2017,Abolfathi:2017}), a
component of the Sloan Digital Sky Survey IV (\sdssiv;
\citealt{Gunn:2006,Blanton:2017}).
\apogee\ is designed to map stars across much of the Milky Way by obtaining
high-resolution ($R \sim 22,500$) infrared ($H$-band) spectroscopy of primarily
\RGB\ stars.
Targets are selected with simple color and brightness cuts, but the survey uses
fiber-plugged plates with a maximum of 300 fibers per each $\approx
1.5~\textrm{deg}^2$ field of view, leading to ``pencil-beam''-like sampling of
the Galactic stellar distribution.
In order to meet signal-to-noise ratio requirements, most \apogee\ stars are
observed multiple times in a series of ``visits,'' typically with at least one
visit separated by a month or more in order to help identify binary stars.

@@

For every source in the sample of \apogee\ stars defined in
\sectionname~\ref{sec:data}, we obtain a posterior sampling in binary-system
parameter space, treating it as a single-lined (SB1) spectroscopic binary system
with a single companion.
This sampling is performed with \thejoker\ (\citealt{Price-Whelan:2017}) under a
relatively uninformative prior \pdf, and the resulting posterior samplings are
used to discover and characterize individual binary-star systems and generate a
catalog of companions.
We now describe the assumptions and method used to generate samplings for
individual systems:
\begin{description}
\item[no multiplets] All radial-velocity variations of the primary star are
  induced by a single companion.
  This is motivated by the idea that triple star systems are usually
  hierarchical so that the period of the inner binary is typically much shorter
  than the orbital period of the outer body (e.g., \citealt{Tokovinin:2018}).
  At present, we ignore the possibility of higher-order multiple systems.
  % \todo{revisit this - do we want to also sample over a long-term trend?}
\item[Kepler] All velocity variations of the primary
  are gravitational, and we therefore ignore the possibility of coherent
  intrinsic variation from, e.g., stellar oscillations.
\item[SB1] All spectra are single-lined; that is, we assume that the secondary
  is significantly fainter and is thus undetected in the spectra.
  This assumption is motivated by the fact that we expect \RGB\ stars to be
  substantially more luminous than their typical companion.
  However, there are known main-sequence double-lined binary stars in the
  \apogee\ catalog (\citealt{El-Badry:2018}), and an expected but unknown
  fraction of \RGB--\RGB\ binaries.
\item[simple noise model] Measurements are unbiased and noise estimates are
  correct up to an unknown excess variance.
  All noise contributions result in Gaussian uncertainties on the individual
  radial-velocity measurements.
\end{description}

@@

For all \nstars\ \apogee\ stars with $\geq 3$ good visits (see
\sectionname~\ref{sec:data}), we use \thejoker\ to generate posterior samplings
for each star under the assumptions listed above (see
\sectionname~\ref{sec:fitting}).
We start by generating a library of \nprior\ prior samples generated under a
prior similar to that defined in \citet{Price-Whelan:2017}:
\begin{itemize}
    \item uniform or isotropic in angle parameters,
    \item uniform in log-period over the domain $[1,32768]~\textrm{day}$,
    \item a beta distribution over eccentricity (using parameters from
    \citealt{Kipping:2013}).
\end{itemize}
For the excess variance parameter, $s^2$, we use a Gaussian over the transformed
parameter $y = \ln s^2$ with the mean and standard deviation $(\mu_y, \sigma_y)$
indicated where the runs are described (see \sectionname~\ref{sec:catalogs}).
The reference time for each star is set to the minimum visit epoch; $M_0$ then
becomes the mean anomaly at the first visit observation.
\tablename~\ref{tbl:params} contains descriptions of all parameters and priors
used.

@@

We request \nposterior\ posterior samples for each source.
Depending on the data quality and phase coverage of the visits, \thejoker\ will
require different numbers of prior samples in order to rejection sample down to
the requested number of posterior samples: For few-epoch or noisy RV data, many
prior samples will pass the rejection step, whereas for very precise or
many-epoch RV data, \thejoker\ may need to process the full library of prior
samples.
We therefore generate the posterior samples using an iterative procedure that
adaptively predicts how many prior samples to test for each star.
For sources with very constraining data, \thejoker\ may return fewer than the
requested number of samples (as few as one sample).
When this occurs, we continue sampling either using standard MCMC, or by
increasing the size of the prior cache and continuing rejection sampling with
\thejoker.

@@

However, there are a number of caveats to keep in mind about this estimate of
the excess variance distribution.
First, we do not remove triple or other multiple systems: For any individual
system, the radial velocity variations induced by other massive bodies will lead
to larger preferred values for the excess variance parameter.
We don't expect there to be a large number of triple systems in our sample, but
this is still an important consideration for future efforts.
Second, we are sensitive to outliers and very non-Gaussian systematic error
distributions.
We later assess the non-Gaussianity of the visit velocity uncertainties by
looking at the visit velocity residuals away from the orbit samples produced by
\thejoker\ using the updated excess variance distribution (see
\sectionname~\ref{sec:discuss-assumptions}).

@@

We don't expect a sharp transition in inferred orbital parameters between stars
with companions and stars without companions: There is a continuum of companion
properties.
For example, the companions can be low mass, or at long periods, or at high
inclination, all of which will make the velocity semi-amplitude, $K$, small for
a given system.
Therefore there is no simple cut on radial velocity data alone that would select
a complete sample of stars with companions.
It is nevertheless possible to define a cut that selects stars with
high-confidence companions.

@@

A subset of the high-$K$ sample (\sectionname~\ref{sec:catalog-confident}) have
multimodal posterior distributions over orbital parameters that are limited to
a few qualitatively different solutions.
For these stars, one or a few more RV measurements would likely lead to
uniquely-determined orbital parameters; These stars are prime candidates for
follow-up efforts.
As examples of such cases, we include an additional catalog of systems that have
effectively bimodal posterior samplings in orbital period.
We identify these systems using $k$-means clustering (\citealt{Lloyd:1982}) of
the posterior samples in period.
In detail, for all stars in the high-$K$ sample, we compute $\ln P$ for all
period samples, then use $k$-means clustering with $k=2$ as implemented in the
\texttt{scikit-learn} package (\citealt{Pedregosa:2011}) to identify two
clusters of samples.
We initialize the cluster positions at either end of the range of possible
periods.
For each cluster, we then ask whether the samples assigned to that cluster are
unimodal (\eqname~\ref{eq:unimodal}).
If the samples in each respective cluster are unimodal, we call the sampling
``bimodal''; \nbimodal\ systems are identified as bimodal.

@@

Paradoxically, there exist short period ($\lesssim 100~\textrm{day}$) companions
at low surface gravities ($\logg \lesssim 1$), obvious in the lower-left panel
of \figurename~\ref{fig:logg-teff-p-e}: These companions would orbit within the
surface of their primary stars.
Each of these systems appears fine from the \apogee\ data quality flags, but
could nonetheless have incorrect stellar parameters.
As a test, we would ideally be able to compare the spectroscopic stellar
parameters to an independent determination from, e.g., asteroseismology.
Unfortunately, none of these short-period, low-\logg\ stars in the unimodal or
bimodal samples appear in the \acronym{APOKASC} (\citealt{Serenelli:2017})
catalog, which provides asteroseismic stellar parameters for a few hundred
\apogee\ dwarf and giant stars.
We therefore instead cross-match all high-$K$ stars with $\logg < 1$ and $99\%$
of their period samples below $100~\textrm{day}$ to the \acronym{APOKASC}
catalog: One star appears in both samples 2M19024490+4419523.
In \apogee\ \DR, this star has $\logg = 0.57$, but asteroseismic $\logg > 4$
(e.g., \texttt{HUBER\_LOGG}), consistent with being an M dwarf.
Many of these systems could therefore be low-mass dwarf stars with incorrect
stellar parameters in \apogee\ \DR.

@@

It is important to keep in mind that the companion catalogs and results
presented in this \documentname\ depend on the assumptions laid out in
\sectionname~\ref{sec:fitting}.
We have only considered radial velocity modulations from a single massive
companion---\emph{no multiplets}; This is a fundamental limitation of our search
and methodology.
However, stars with multiple companions will likely be included in our companion
catalog anyway, only with two-body orbital solutions that either don't fit the
data well or pick out the shortest period orbit.

@@

Of the 382 companions released as a part of the previous search, only 188 of the
host stars passed the stellar parameter and quality cuts used to define the
parent sample in this work (see \sectionname~\ref{sec:data}).
We have looked at all of the overlapping stars to compare the previously derived
companion orbital properties to the posterior samplings derived with \thejoker.
We find that the comparisons fall in three categories:
(1) the parameters reported in \citet{Troup:2016} agree with the posterior
samplings, and the period distribution appears unimodal,
(2) the parameters reported in \citet{Troup:2016} identify one possible mode of
a likely multi-modal posterior \pdf\ over orbital parameters, and
(3) the data changed significantly between \apogee\ \DRtw\ and \DR, so
no meaningful comparisons can be made; Roughly 1/3 of the comparison sample
falls into each class.
\figurename~\ref{fig:troup-unimodal} shows a few representative cases in which
the \citet{Troup:2016} orbital parameters (orbit shown as orange line in left
panels, parameters shown as orange + in right panels) is consistent with the
orbit samples from \thejoker.
\figurename~\ref{fig:troup-multimodal} shows a few representative cases in which
we find that the posterior \pdf\ over orbital parameters is multimodal, and the
\citet{Troup:2016} orbit identifies one of these modes.
For completeness, \figurename~\ref{fig:troup-datachanged} shows two instances in
which the orbital parameters from \citet{Troup:2016} no longer make sense,
likely because the data changed between data releases.

@@

We have selected a catalog of nearly 5,000 stellar systems with companions by
making cuts on posterior beliefs about the amplitude of orbital radial velocity
variations for often low-epoch, sparsely sampled radial velocity data.
We provide posterior samplings over orbital parameters for all \nstars\ in the
parent sample of \apogee\ \DR\ systems used in this work, along with several
sub-catalogs with better constrained orbital information:
\begin{itemize}
    \item A catalog of \nunimodal\ systems with unimodal posterior samplings,
    and therefore uniquely determined orbits, of which 227 are newly discovered
    binary star systems.
    \item A catalog of \nbimodal\ systems with highly constrained posterior
    samplings that, in period, span two distinct period modes.
    For these systems, one or a few more radial velocity measurements would
    uniquely determine their orbits.
    79 of these systems are newly discovered binary star systems.
    \item A catalog of \nhighK\ systems with radial velocity variations
    consistent with having a companion, but which need further radial velocity
    measurements to better constrain the orbital properties.
\end{itemize}
All companion catalogs described in this work (\sectionname~\ref{sec:catalogs})
are available online at \todo{XX}.

@@

>>>>

\begin{abstract}\noindent % trust me
% Context
Multi-epoch radial velocity measurements of stars can be used to identify
stellar, sub-stellar, and planetary-mass companions.
Even a small number of observation epochs can be informative about
companions, though there can be multiple qualitatively different orbital
solutions that fit the data.
We have custom-built a Monte Carlo sampler (\thejoker) that delivers reliable
(and often highly multi-modal) posterior samplings for companion orbital
parameters given sparse radial-velocity data.
% Aims
Here we use \thejoker\ to perform a search for companions to \nstars\ red-giant
stars observed in the \apogee\ survey (\DR) with $\geq 3$ spectroscopic epochs.
% Methods
We select stars with probable companions by making a cut on our posterior belief
about the amplitude of the stellar radial-velocity variation induced by the
orbit.
% Results
We provide (1)~a catalog of \nunimodal\ companions for which the stellar
companion properties can be confidently determined, (2)~a catalog of \nhighK\
stars that likely have companions, but would require more observations to
uniquely determine the orbital properties, and (3)~posterior samplings for the
full orbital parameters for all stars in the parent sample.
We highlight interesting systems and show the characteristics of systems with
confidently determined companion properties.
\end{abstract}

@@

We have solved the problem of deriving comprehensive multi-modal \pdf\ samplings
previously with \thejoker\ (\citealt{Price-Whelan:2017}), a Monte Carlo
rejection sampler that is computationally expensive but probabilistically
righteous:
It delivers independent posterior \pdf\ samples for single-companion binary
orbital parameters, given any number of radial-velocity measurements.
Here we use \thejoker\ to generate posterior \pdf\ samples for stars observed by
the \apogee\ survey (see \sectionname~\ref{sec:data}; \citealt{Majewski:2017}).

@@

The \apogee\ surveys primarily target red-giant-branch (\RGB) and other evolved
stars (e.g., red clump giants, RC), which are ideal for the study of single-line
binary systems.
In general, they are unlikely to have comparably-bright companions, and their
spectra are therefore fit as single-line objects.
When this constraint is not met, \thejoker\ will in general fail, and a model
that fits for a mixture of stellar spectra is more appropriate (e.g.,
\citealt{El-Badry:2018}).
The subset of RC stars are even more powerful as they are standard candles and
have masses that can be estimated using spectroscopy (using dredged-up elements;
\citealt{Martig:2016,Ness:2016}).
With mass estimates for the primary star, the binary-orbit fitting will return
$M_2\,\sin i$ (minimum mass) estimates for the secondary, and not just estimates
of the so-called ``binary mass function.''
Additionally, the \apogee\ pipelines (\citealt{Garcia-Perez:2016}) and also
\thecannon\ (\citealt{Ness:2015}) produce detailed abundance estimates for \RGB\
and \RC\ stars.
If there are causal relationships between chemical abundances and binary
companions---as are expected---these should be measurable.

@@

All data used in this work come from the publicly-available data release 14
(\DR) of the \apogee\ survey (\citealt{Majewski:2017,Abolfathi:2017}), a
component of the Sloan Digital Sky Survey IV (\sdssiv;
\citealt{Gunn:2006,Blanton:2017}).
\apogee\ is designed to map stars across much of the Milky Way by obtaining
high-resolution ($R \sim 22,500$) infrared ($H$-band) spectroscopy of primarily
\RGB\ stars.
Targets are selected with simple color and brightness cuts, but the survey uses
fiber-plugged plates with a maximum of 300 fibers per each $\approx
1.5~\textrm{deg}^2$ field of view, leading to ``pencil-beam''-like sampling of
the Galactic stellar distribution.
In order to meet signal-to-noise ratio requirements, most \apogee\ stars are
observed multiple times in a series of ``visits,'' typically with at least one
visit separated by a month or more in order to help identify binary stars.

@@

For every source in the sample of \apogee\ stars defined in
\sectionname~\ref{sec:data}, we obtain a posterior sampling in binary-system
parameter space, treating it as a single-lined (SB1) spectroscopic binary system
with a single companion.
This sampling is performed with \thejoker\ (\citealt{Price-Whelan:2017}) under a
relatively uninformative prior \pdf, and the resulting posterior samplings are
used to discover and characterize individual binary-star systems and generate a
catalog of companions.
We now describe the assumptions and method used to generate samplings for
individual systems:
\begin{description}
\item[no multiple companions] All radial-velocity variations of the primary
  star are induced by a single companion.
  This is motivated by the idea that triple star systems are usually
  hierarchical so that the period of the inner binary is typically much shorter
  than the orbital period of the outer body (e.g., \citealt{Tokovinin:2018}).
  At present, we ignore the possibility of higher-order multiple systems.
  % \todo{revisit this - do we want to also sample over a long-term trend?}
\item[Kepler] All velocity variations of the primary
  are gravitational, and we therefore ignore the possibility of coherent
  intrinsic variation from, e.g., stellar oscillations.
\item[SB1] All spectra are single-lined; that is, we assume that the secondary
  is significantly fainter and is thus undetected in the spectra.
  This assumption is motivated by the fact that we expect \RGB\ stars to be
  substantially more luminous than their typical companion.
  However, there are known main-sequence double-lined binary stars in the
  \apogee\ catalog (\citealt{El-Badry:2018}), and an expected but unknown
  fraction of \RGB--\RGB\ binaries.
\item[simple noise model] Measurements are unbiased and noise estimates are
  correct up to an unknown excess variance.
  All noise contributions result in Gaussian uncertainties on the individual
  radial-velocity measurements.
\end{description}

@@

For all \nstars\ \apogee\ stars with $\geq 3$ good visits (see
\sectionname~\ref{sec:data}), we use \thejoker\ to generate posterior samplings
for each star under the assumptions listed above (see
\sectionname~\ref{sec:fitting}).
We start by generating a library of \nprior\ prior samples generated under a
prior similar to that defined in \citet{Price-Whelan:2017}:
\begin{itemize}
    \item uniform or isotropic in angle parameters,
    \item uniform in log-period over the domain $[1,32768]~\textrm{day}$,
    \item a beta distribution over eccentricity (using parameters from
    \citealt{Kipping:2013}).
\end{itemize}
For the excess variance parameter, $s^2$, we use a Gaussian over the transformed
parameter $y = \ln s^2$ with the mean and standard deviation $(\mu_y, \sigma_y)$
indicated where the runs are described (see \sectionname~\ref{sec:catalogs}).
The reference time for each star is set to the first visit epoch; $M_0$ then
becomes the mean anomaly at the first visit observation.
\tablename~\ref{tbl:params} contains descriptions of all parameters and priors
used.

@@

We request \nposterior\ posterior samples for each source.
Depending on the data quality and phase coverage of the visits, \thejoker\ will
require different numbers of prior samples in order to rejection-sample down to
the requested number of posterior samples: For few-epoch or noisy RV data, many
prior samples will pass the rejection step, whereas for very precise or
many-epoch RV data, \thejoker\ may need to process the full library of prior
samples.
We therefore generate the posterior samples using an iterative procedure that
adaptively predicts how many prior samples to test for each star.
For sources with very constraining data, \thejoker\ may return fewer than the
requested number of samples (as few as one sample).
When this occurs, we continue sampling either using standard MCMC, or by
increasing the size of the prior cache and continuing rejection sampling with
\thejoker.

@@

However, there are a number of caveats to keep in mind about this estimate of
the excess variance distribution.
First, we do not remove triple or other multiple systems: For any individual
system, the radial velocity variations induced by other massive bodies will lead
to larger preferred values for the excess variance parameter.
We do not expect there to be a large number of triple systems in our sample, but
this is still an important consideration for future efforts.
Second, we are sensitive to outliers and very non-Gaussian systematic error
distributions.
We later assess the non-Gaussianity of the visit velocity uncertainties by
looking at the visit velocity residuals away from the orbit samples produced by
\thejoker\ using the updated excess variance distribution (see
\sectionname~\ref{sec:discuss-assumptions}).

@@

We do not expect a sharp transition in inferred orbital parameters between stars
with and without companions: There is a continuum of companion properties.
For example, the companions can be low mass, or at long periods, or at high
inclination, all of which will make the velocity semi-amplitude, $K$, small for
a given system.
Therefore, there is no simple cut on radial velocity data alone that would
select a complete sample of stars with companions.
It is nevertheless possible to define a cut that selects stars with
high-confidence companions.

@@

A subset of the high-$K$ sample (\sectionname~\ref{sec:catalog-confident}) have
multimodal posterior distributions over orbital parameters that are limited to
a few qualitatively different solutions.
For these stars, one or a few more RV measurements would likely lead to
uniquely-determined orbital parameters, making these stars prime candidates for
follow-up efforts.
As examples of such cases, we include an additional catalog of systems that have
effectively bimodal posterior samplings in orbital period.
We identify these systems using $k$-means clustering (\citealt{Lloyd:1982}) of
the posterior samples in period.
In detail, for all stars in the high-$K$ sample, we compute $\ln P$ for all
period samples, then use $k$-means clustering with $k=2$ as implemented in the
\texttt{scikit-learn} package (\citealt{Pedregosa:2011}) to identify two
clusters of samples.
We initialize the cluster positions at either end of the range of possible
periods.
For each cluster, we then ask whether the samples assigned to that cluster are
unimodal (\eqname~\ref{eq:unimodal}).
If the samples in each respective cluster are unimodal, we call the sampling
``bimodal''; \nbimodal\ systems are identified as bimodal.

@@

Paradoxically, there appear to exist short period ($\lesssim 100~\textrm{day}$)
companions at low surface gravities ($\logg \lesssim 1$), obvious in the
lower-left panel of \figurename~\ref{fig:logg-teff-p-e}: These companions would
orbit within the surface of their primary stars.
Each of these systems appears fine from the \apogee\ data quality flags, but
could nonetheless have incorrect stellar parameters.
As a test, we would ideally be able to compare the spectroscopic stellar
parameters to an independent determination from, e.g., asteroseismology.
Unfortunately, none of these short-period, low-\logg\ stars in the unimodal or
bimodal samples appear in the \acronym{APOKASC} (\citealt{Serenelli:2017})
catalog, which provides asteroseismic stellar parameters for a few hundred
\apogee\ dwarf and giant stars.
We therefore instead cross-match all high-$K$ stars with $\logg < 1$ and $99\%$
of their period samples below $100~\textrm{day}$ to the \acronym{APOKASC}
catalog: One star appears in both samples 2M19024490+4419523.
In \apogee\ \DR, this star has $\logg = 0.57$, but asteroseismic $\logg > 4$
(e.g., \texttt{HUBER\_LOGG}), consistent with being an M dwarf.
Many of these systems could therefore be low-mass dwarf stars with incorrect
stellar parameters in \apogee\ \DR.

@@

It is important to keep in mind that the companion catalogs and results
presented in this \documentname\ depend on the assumptions laid out in
\sectionname~\ref{sec:fitting}.
We have only considered radial velocity modulations from a single massive
companion---\emph{no multiple companions}; This is a fundamental limitation of
our search and methodology.
However, stars with multiple companions will likely be included in our companion
catalog anyway, only with two-body orbital solutions that either don't fit the
data well or pick out the shortest period orbit.

@@

Of the 382 companions released as a part of the \citet{Troup:2016} search, only
188 of the host stars passed the stellar parameter and quality cuts used to
define the parent sample in this work (see \sectionname~\ref{sec:data}).
We have looked at all of the overlapping stars to compare the previously derived
companion orbital properties to the posterior samplings derived with \thejoker.
We find that the comparisons fall in three categories:
(1) the parameters reported in \citet{Troup:2016} agree with the posterior
samplings, and the period distribution appears unimodal,
(2) the parameters reported in \citet{Troup:2016} identify one possible mode of
a likely multi-modal posterior \pdf\ over orbital parameters, and
(3) the radial velocity data used in \citet{Troup:2016} changed significantly
between \apogee\ \DRtw\ and \DR, so no meaningful comparisons can be made;
roughly 1/3 of the comparison sample falls into each class.
\figurename~\ref{fig:troup-unimodal} shows a few representative cases in which
the \citet{Troup:2016} orbital parameters (orbit shown as orange line in left
panels, parameters shown as orange + in right panels) is consistent with the
orbit samples from \thejoker.
\figurename~\ref{fig:troup-multimodal} shows a few representative cases in which
we find that the posterior \pdf\ over orbital parameters is multimodal, and the
\citet{Troup:2016} orbit identifies one of these modes.
For completeness, \figurename~\ref{fig:troup-datachanged} shows two instances in
which the orbital parameters from \citet{Troup:2016} no longer make sense,
likely because the data changed between data releases.

@@

We have selected a catalog of nearly 5,000 stellar systems with companions by
making cuts on posterior beliefs about the amplitude of orbital radial velocity
variations for often low-epoch, sparsely sampled radial velocity data.
We provide posterior samplings over orbital parameters for all \nstars\ in the
parent sample of \apogee\ \DR\ systems used in this work, along with several
sub-catalogs with better constrained orbital information:
\begin{itemize}
    \item A catalog of \nunimodal\ systems with unimodal posterior samplings,
    and therefore uniquely determined orbits, of which 225 are newly discovered
    binary star systems.
    \item A catalog of \nbimodal\ systems with highly constrained posterior
    samplings that, in period, span two distinct period modes.
    For these systems, one or a few more radial velocity measurements would
    uniquely determine their orbits.
    90 of these systems are newly discovered binary star systems.
    \item A catalog of \nhighK\ systems with radial velocity variations
    consistent with having a companion, but which need further radial velocity
    measurements to better constrain the orbital properties.
\end{itemize}
All companion catalogs described in this work (\sectionname~\ref{sec:catalogs})
are available online at \todo{XX}.

@@

HWR acknowledges support by Sonderforschungsbereich SFB 881 (A3) of the German
Research Foundation (DFG), and from the European Research Council under the
European Union’s Seventh Framework Programme (FP 7) ERC Grant Agreement
n. [321035].
